Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
more g1

The final example in \figurename~\ref{fig:prog-g1} consists of two
part: \texttt{g1} creates a closure with one variable $x$ in its
environment and \texttt{f4} as the code. When the closure is called,
it expects to be called with a capability for a callback and a stack
capability.

@@

\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
g1:  malloc $r_2$ 1
     store $r_2$ 0
     move $\pcreg$ $r_3$
     lea $r_3$ $\var{offset}$
     crtcls $[(x, r_2)]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
     jmp $r_0$
f4:  reqglob $r_1$
     prepstack $r_\stk$
     store $x$ 0
     scall $r_1$($[]$,$[r_0,r_1,r_{\var{env}}]$)
     store $x$ 1
     scall $r_1$($[]$,$[r_0,r_{\var{env}}]$)
     load $r_1$ x
     assert $r_1$ 1
     mclear $r_\stk$
     rclear $\RegName \setminus \{r_0,\pcreg\}$
     jmp $r_0$
\end{lstlisting}
  \caption{A program that relies on well-bracketedness of
    \texttt{scall}s to function correctly. $\var{offset}$ is the
    offset to $f4$.}
  \label{fig:prog-g1}
\end{figure}

>>>>

The final example in \figurename~\ref{fig:prog-g1} consists of two
part: \texttt{g1} is a closure generation program with one variable $x$ in its
environment and \texttt{f4} as the code. Like in the previous example, the assertion can fail if the adversary can capture the protected return pointer of the second call, invoke the closure anew and use the captured protected return pointer in the first call when the variable $x$ has the value 0.

In the other examples, the known program started the execution and called an unknown piece of code. In this example, the control is inverted, so an unknown piece of code gets an enter capability for the closure creator.

@@

\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
g1:  malloc $r_2$ 1
     store $r_2$ 0
     move $\pcreg$ $r_3$
     lea $r_3$ $\var{offset}$
     crtcls $[(x, r_2)]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
     jmp $r_0$
f4:  reqglob $r_1$
     prepstack $r_\stk$
     store $x$ 0
     scall $r_1$($[]$,$[r_0,r_1,r_{\var{env}}]$)
     store $x$ 1
     scall $r_1$($[]$,$[r_0,r_{\var{env}}]$)
     load $r_1$ $x$
     assert $r_1$ 1
     mclear $r_\stk$
     rclear $\RegName \setminus \{r_0,\pcreg\}$
     jmp $r_0$
\end{lstlisting}
  \caption{A program that relies on well-bracketedness of
    \texttt{scall}s to function correctly. $\var{offset}$ is the
    offset to $f4$.}
  \label{fig:prog-g1}
\end{figure}
